PyTracer: Automatically profiling numerical instabilities in Python

### 2022-04-14 preprint/paper.tex
Revision

\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{todonotes}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{xcolor,colortbl}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue!50!black,citecolor=blue!75!black,filecolor=black,urlcolor=blue!75!black}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage{makecell}
\usepackage{ulem} % provides sout
\usepackage[frozencache=true,cachedir=minted-cache]{minted} 
\usepackage[htt]{hyphenat}      
\usepackage{subcaption}
\usepackage{graphicx,import}
\usepackage{booktabs}

@@

\title{PyTracer: Automatically profiling numerical instabilities in Python}
\author{Yohan Chatelain$^1$, Nigel Young$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
$^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
$^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
    \date{}
\maketitle

>>>>

\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{xcolor,colortbl}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue!50!black,citecolor=blue!75!black,filecolor=black,urlcolor=blue!75!black}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage{makecell}
\usepackage{ulem} % provides sout
\usepackage[frozencache=true,cachedir=minted-cache]{minted} 
\usepackage[htt]{hyphenat}      
\usepackage{subcaption}
\usepackage{graphicx,import}
\usepackage{booktabs}

@@

\title{PyTracer: Automatically profiling numerical instabilities in Python}
\author{Yohan Chatelain$^1$, Nigel Yong$^1$,  Gregory Kiar$^2$,  Tristan Glatard$^1$\\
$^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
$^2$Center for the Developing Brain, Child Mind Institute, New York, NY, USA}
\date{\textit{This work has been submitted to the IEEE for possible publication. 
Copyright may be transferred without notice, after which this version may no 
longer be accessible.}}
\maketitle
